Preprocessing

### 2023-08-10 docs/presentation/preprocess.Rmd
viz: q8 pre-calculate

## Save
```{r}
analysis %>%
  saveRDS("data/analysis.rds", compress = FALSE)
```

>>>>

## Q8 Likert
```{r}
q8_to_likert <- function(data = analysis) {
  data %>%
    # make data for likert
    pivot_longer(cols = starts_with("Q8")) %>%
    group_by(name, value) %>%
    summarise(n = n()) %>%
    mutate(value = factor(value, levels = agree_levels)) %>%
    replace_na(list(value = "Don't know")) %>%
    group_by(name) %>%
    mutate(perc = n / sum(n)) %>%
    mutate(
      yeah = ifelse(any(value == "Agree"), perc[value == "Agree"], 0),
      idk = ifelse(any(value == "Don't know"), perc[value == "Don't know"] / 2, 0),
      nah = ifelse(any(value == "Disagree"), perc[value == "Disagree"], 0),
      start = case_match(
        value,
        "Strongly agree" ~ yeah + idk,
        "Agree" ~ idk,
        "Don't know" ~ -idk,
        "Disagree" ~ -idk - perc,
        "Strongly disagree" ~ -idk - nah - perc,
      )
    ) %>%
    ungroup() %>%
    dplyr::select(-c(yeah, nah, idk))
}
```

```{r Q8}
q8_q3 <- map(
  subfields, ~ analysis %>%
    filter(Q3_recoded == .x) %>%
    q8_to_likert()
) %>%
  set_names(subfields)

q8_q4 <- map(
  types, ~ analysis %>%
    filter(Q4 == .x) %>%
    q8_to_likert()
) %>%
  set_names(types)

q8 <- append(q8_q3, q8_q4)
q8$Everyone <- q8_to_likert()
saveRDS(q8, file = "data/q8.rds")
```

## Save
```{r}
analysis %>%
  saveRDS("data/analysis.rds")
```
